Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System

### 2022-12-10 paper-kelompok/main.tex
rev2

\begin{abstract}
We have proposed a portable visible spectrophotometer with an ability to integrate with a particular digital microfluidic (DMF) system.
An interface, consisted of an LCD and a set of buttons, allowed users to gather and view measurement results in a continous manner.
The device had a dimension of 120 x 131 x 207 mm and had a weight of 832 g.
The device measured absorbance in the wavelength range of 400 to 700 nm with a resolution of 0.77 nm.
The device was tested by assessing the accuracy and repeatability of the transmission and wavelength measurements, as well as the wavelength resolution.
The results showed generally good performance compared with a research-grade commercial spectrophotometer.
\end{abstract}

@@

Based on Fig. \ref{glucose_peak_wavelength}, out of 10 measurement iterations, the maximum peak wavelength occurs at 521.76 nm, with the minimum peak wavelength at 519.46 nm.
On average, the peak wavelength that occurs is 521.07 nm, indicated by a black line on the graph.
From this data, the standard deviation of the average wavelength is at +0.63 nm, with a maximum deviation of +0.69 nm and a minimum deviation of -1.61.

>>>>

\begin{abstract}
We have proposed a portable visible spectrophotometer with an ability to integrate with a particular digital microfluidic (DMF) system.
An interface, consisted of an LCD and a set of buttons, allowed users to gather and view measurement results in a continous manner.
The device had a dimension of 120 x 131 x 207 mm and had a weight of 832 g.
The device measured absorbance in the wavelength range of 400 to 700 nm with a resolution of 0.77 nm.
The device was tested by assessing the accuracy and repeatability of the transmission and wavelength measurements, as well as the wavelength resolution.
The transmittance RMSE was ±11.22\% with ±9.88 nm wavelength error.
The device had a transmittance repeatability of ±2.58\% and wavelength repeatability of ±0.63 nm.
\end{abstract}

@@

Based on Fig. \ref{glucose_peak_wavelength}, out of 10 measurement iterations, the maximum peak wavelength occurs at 521.76 nm, with the minimum peak wavelength at 519.46 nm.
On average, the peak wavelength that occurs is 521.07 nm, indicated by a black line on the graph.
From this data, the standard deviation of the average wavelength is at 0.63 nm, with a minimum deviation of 0.69 nm and a minimum deviation of 1.61 nm.
